Analyzing MLG distribution

### 2017-06-28 doc/RMD/MLG-distribution.Rmd
rerun with correct locus configuration
This ensures the MLGs are the same as the paper.
Save figures as pdf instead of svg

```{r}
load("data/sclerotinia_16_loci.rda")
setPop(dat) <- ~Region
dat
locNames(dat)
other(dat)$REPLEN
head(other(dat)$meta)
keeploci <- !locNames(dat) %in% colnames(corrected_loci)
dat11 <- dat[loc = keeploci, mlg.reset = TRUE] # reducing to 11 loci and recalculating mlgs
dat11
```

@@

```{r graph-16-loci, fig.width = 7, fig.height = 7}
par(mfrow = c(1, 1))
(g16o <- cluster_optimal(graph16loc$total))
plot_mlg_graph(graph16loc$total, alt_layout) + labs(list(subtitle = "(16 loci)"))
ggsave(filename = "results/figures/publication/FigureS1Z.svg", width = 88, height = 88, units = "mm", scale = 2)
```

@@

```{r graph-11-loci, fig.width = 7, fig.height = 7}
(g11o <- cluster_optimal(graph11loc$total))
plot_mlg_graph(graph11loc$total, alt_layout) + labs(list(subtitle = "(11 loci)"))
ggsave(filename = "results/figures/publication/Figure3Z.svg", width = 88, height = 88, units = "mm", scale = 2)
```

>>>>

```{r}
load("data/sclerotinia_16_loci.rda")

@@

```{r graph-16-loci, fig.width = 7, fig.height = 7}
par(mfrow = c(1, 1))
(g16o <- cluster_optimal(graph16loc$total))
plot_mlg_graph(graph16loc$total, alt_layout) + labs(list(subtitle = "(16 loci)"))
ggsave(filename = "results/figures/publication/FigureS1Z.pdf", width = 88, height = 88, units = "mm", scale = 2)
```

@@

```{r graph-11-loci, fig.width = 7, fig.height = 7}
(g11o <- cluster_optimal(graph11loc$total))
plot_mlg_graph(graph11loc$total, alt_layout) + labs(list(subtitle = "(11 loci)"))
ggsave(filename = "results/figures/publication/Figure3Z.pdf", width = 88, height = 88, units = "mm", scale = 2)
```
